---
title: "Homework 1"
date: 2020-09-16
author: "Michelle Lee"
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```

##Problem 1
create a dataframe
```{r}
p1_df = 
  tibble(
    samp=rnorm(10),
    samp_gt_0 = samp>0,
    char_vec =c("a","b","c","d","e","f","g","h","i","j"), 
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
)
p1_df
```

mean of each variable: 

I'm able to print the mean of samp and samp_gt_0, but not char_vec and factor_vec. This is due to the fact that samp and samp_gt_0 are numbers, which we can calculate the average of these variables. However, char_vec and factor_vec are words, and we can't calculate means of words.

```{r}
mean(pull(p1_df,samp))
mean(pull(p1_df,samp_gt_0))
mean(pull(p1_df,char_vec))
mean(pull(p1_df,factor_vec))
```
applying as.numeric:

```{r}
as.numeric(pull(p1_df,samp))
as.numeric(pull(p1_df,samp_gt_0))
as.numeric(pull(p1_df,char_vec))
as.numeric(pull(p1_df,factor_vec))
```


In some cases, you can explicitly convert variables from one type to another. Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?

In a second code chunk:

convert the logical vector to numeric, and multiply the random sample by the result
convert the logical vector to a factor, and multiply the random sample by the result
convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
Problem 2
##Problem 2
