---
title: "Homework 1"
date: 2020-09-16
author: "Michelle Lee"
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```

##Problem 1
create a dataframe
```{r create df}
p1_df = 
  tibble(
    samp=rnorm(10),
    samp_gt_0 = samp>0,
    char_vec =c("a","b","c","d","e","f","g","h","i","j"), 
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
)
p1_df
```

```{r create mean}
samp= (pull(p1_df,samp))
logical = pull(p1_df,samp_gt_0)
char = pull(p1_df,char_vec)
factor = pull(p1_df,factor_vec)

mean(samp)
mean(logical)
mean(char)
mean(factor)
```

mean of each variable: 

I'm able to print the mean of samp and samp_gt_0, but not char_vec and factor_vec. This is due to the fact that samp and samp_gt_0 are numbers, which we can calculate the average of these variables. However, char_vec and factor_vec are words, and we can't calculate means of words.

applying as.numeric:

this function shows why the average of samp_gt_0 was 0.5, and why average of charcter variable could not be calculated. 
```{r convert to numeric, results = "hide"}
as.numeric(logical)
as.numeric(char)
as.numeric(factor)
```
converting logical vertor to numeric*samp

```{r second chunk}
as.numeric(logical)*samp
as.factor(logical)*samp
as.numeric(as.factor(logical))*samp
```

##Problem 2
downloading penguins dataset
```{r}
install.packages("palmerpenguins")
data("penguins", package = "palmerpenguins")

```
